---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# crimemappingdata

<!-- badges: start -->
<!-- badges: end -->

The crimemappingdata package contains a variety of datasets that are useful in learning crime mapping. These datasets are used in the [crimemapping package](https://github.com/mpjashby/crimemapping/) but are also available for use by anyone else in accordance with the licence shown in the documentation for each dataset.



## Installation

You can install the development version of crimemappingdata from [GitHub](https://github.com/mpjashby/crimemappingdata/) with:

```r
# install.packages("remotes")
remotes::install_github("mpjashby/crimemappingdata")
```


## Available datasets

The following datasets are available, both as: 

  * R data that can be called using the `data()` function, e.g. `data(aggravated_assaults)`, and
  * stand-alone files that can be downloaded in the formats shown below.
  
See the manual page for each dataset (e.g. `?aggravated_assaults`) for the corresponding stand-alone file URL. Different stand-alone datasets are provided in different file formats (including spatial and non-spatial formats) to give the opportunity for students to practice loading files of different types (e.g. using `readr::read_csv()` or `readxl::read_excel()`). 

```{r, echo=FALSE}
data_in_package <- as.data.frame(datasets.load::datasets(package = "crimemappingdata"))
data_in_package$Dataset <- data_in_package$Item
data_in_package$Description <- data_in_package$Title

files <- data.frame(file = dir("inst/extdata"))
files$Dataset <- regmatches(files$file, regexpr("[a-z\\_]+", files$file))
files$Format <- paste0(
  "`", 
  regmatches(files$file, regexpr("\\..*$", files$file)), 
  "`"
)
files$file <- NULL

datasets_data <- merge(data_in_package, files, by = "Dataset")

knitr::kable(datasets_data[, c("Dataset", "Description", "Format")])
```

Note that gzipped CSV files (with the file extension `.csv.gz`) can be opened using `readr::read_csv()` and functions from other packages, but not `base::read.csv()`.


## Using the data in teaching

For suggestions on how to use the data in this package for teaching, as well as details of each dataset, see the vignette `vignette("teaching")`.
