---
title: "Summary of available datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summary of available datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, comment = "#>")
```



The `crimemappindata` package contains `r nrow(datasets.load::datasets(package = "crimemappingdata"))` datasets that are designed to be used in teaching crime mapping and crime analysis more generally. There are several different types of data available:

  * Point-level crime data.
  * Area-level crime counts.
  * Supporting data, such as population data and spatial boundaries.

The `crimemappingdata` package is licensed under the MIT Licence, but the individual datasets have been licensed by the data provider using a variety of different open-data licences. Check the manual page for each dataset for details of the relevant licence. Users are responsible for using the data in accordance with the applicable licence for a dataset.


## Point-level crime data


### `aggravated_assaults`

```{r}
data(aggravated_assaults, package = "crimemappingdata")
```

Dataset of `r format(nrow(aggravated_assaults), big.mark = ",")` aggravated assaults in Austin, TX, in 2019.

```{r}
aggravated_assaults |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is different from the package version. The stand-alone version is an Excel file containing three sheets. Each sheet has aggravated-assault data for 2019 for a different city: Austin, TX; Fort Worth, TX; and Seattle, WA. Students can get the same data as is in the package version of the dataset by loading the `Austin` sheet from the Excel file using the [readxl package](https://readxl.tidyverse.org/).


### `bronx_shootings`

```{r}
data(bronx_shootings, package = "crimemappingdata")
data(nyc_shootings, package = "crimemappingdata")
```

Dataset of `r format(nrow(nyc_shootings), big.mark = ",")` shootings in NYC in 2019 and separately of the `r format(nrow(bronx_shootings), big.mark = ",")` of those shootings that occurred in the Bronx.

```{r}
nyc_shootings |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of these datasets are CSV files.


### `cdmx_car_jacking`

```{r}
data("cdmx_car_jacking", package = "crimemappingdata")
```

Dataset of `r format(nrow(cdmx_car_jacking), big.mark = ",")` car jacking offences in Mexico City in 2019.

```{r}
cdmx_car_jacking |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a geopackage file.



### `chicago_aggravated_assaults`

```{r}
data(chicago_aggravated_assaults, package = "crimemappingdata")
```

Dataset of `r format(nrow(chicago_aggravated_assaults), big.mark = ",")` aggravated assaults in Chicago between 2010 and 2019.

```{r}
chicago_aggravated_assaults |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a gzipped CSV file.



### `cincinnati_burglary`

```{r}
data(cincinnati_burglary, package = "crimemappingdata")
```

Dataset of `r format(nrow(cincinnati_burglary), big.mark = ",")` burglaries in Cincinnati, Ohio, between 2016 and 2018.

```{r}
cincinnati_burglary |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a gzipped CSV file.



### `czechia_collisions` and `czechia_mcycle_thefts`

```{r}
data(czechia_collisions, package = "crimemappingdata")
data(czechia_mcycle_thefts, package = "crimemappingdata")
```

Datasets of `r format(nrow(czechia_collisions), big.mark = ",")` traffic collisions related to alcohol or drugs and separately of `r format(nrow(czechia_mcycle_thefts), big.mark = ",")` thefts of two-wheeled motor vehicles in Czechia between 2020 and 2022.

```{r}
czechia_collisions |>
  head(10) |>
  knitr::kable(caption = "`czechia_collisions`")
```

```{r}
czechia_mcycle_thefts |>
  head(10) |>
  knitr::kable(caption = "`czechia_mcycle_thefts`")
```

The stand-alone version of these datasets are geopackage files.



### `downtown_homicides` and `glenrose_heights_homicides`

```{r}
data(downtown_homicides, package = "crimemappingdata")
data(glenrose_heights_homicides, package = "crimemappingdata")
```

Two datasets of homicides in the Downtown and Glenrose Heights neighbourhoods of Atlanta, GA, in 2019. There are four rows in each dataset. The `label` column contains a pre-formatted label suitable for using in plotting the points on a map.

```{r}
downtown_homicides_table <- downtown_homicides
downtown_homicides_table$label <- gsub(
  "\n",
  "<br>",
  downtown_homicides_table$label
)
downtown_homicides_table |>
  head(10) |>
  knitr::kable(caption = "`downtown_homicides`")
```

```{r}
glenrose_heights_homicides_table <- glenrose_heights_homicides
glenrose_heights_homicides_table$label <- gsub(
  "\n",
  "<br>",
  glenrose_heights_homicides_table$label
)
glenrose_heights_homicides_table |>
  head(10) |>
  knitr::kable(caption = "`glenrose_heights_homicides`")
```

The stand-alone versions of these datasets are available as both CSV and geopackage files.


### `hungerford_shootings`

```{r}
data(hungerford_shootings, package = "crimemappingdata")
```

Dataset of the locations of `r format(nrow(hungerford_shootings), big.mark = ",")` shootings during the [Hungerford massacre](https://en.wikipedia.org/wiki/Hungerford_massacre) in 1987. This can be used for teaching mapping of crime series.

```{r}
hungerford_shootings |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a CSV file.


### `lancashire_asb` and `northumbria_asb`

```{r}
data(lancashire_asb, package = "crimemappingdata")
data(northumbria_asb, package = "crimemappingdata")
```

Datasets of `r format(nrow(lancashire_asb), big.mark = ",")` anti-social behaviour incidents in Lancashire and `r format(nrow(northumbria_asb), big.mark = ",")` incidents in Northumbria, England, in 2022.

```{r}
lancashire_asb |>
  head(10) |>
  knitr::kable(caption = "`lancashire_asb`")
```

```{r}
northumbria_asb |>
  head(10) |>
  knitr::kable(caption = "`northumbria_asb`")
```

The stand-alone version of these datasets are tab-separated values (`.tab`) files. The data in these file can be used together with the `lancashire_districts`/`northumbria_districts`, `lancashire_wards`/`northumbria_wards` and `lancashire_ward_pop`/`northumbria_ward_pop` datasets to calculate area-level incidence rates.


### `london_crimes`

```{r}
data(london_crimes, package = "crimemappingdata")
```

Dataset of `r format(nrow(london_crimes), big.mark = ",")` crimes recorded in London in 2022.

```{r}
london_crimes |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a gzipped CSV file.


### `medellin_homicides`

```{r}
data(medellin_homicides, package = "crimemappingdata")
```

Dataset of `r format(nrow(medellin_homicides), big.mark = ",")` homicides in Medellin, Colombia, from 2010 to 2019.

```{r}
medellin_homicides |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a CSV file. Note that the CSV file uses semi colons as column delimiters and commas as decimal separators in numbers, in accordance with Colombian practice. This file can be read with functions such as [readr::read_csv2()].

This dataset can be used together with the `medellin_metro_lines` and `medellin_metro_stns` datasets to teach topics such as finding or counting crimes within a certain distance of a facility (e.g. a metro station).


### `nottingham_burglary` and `nottingham_robbery`

```{r}
data(nottingham_burglary, package = "crimemappingdata")
data(nottingham_robbery, package = "crimemappingdata")
```

Datasets of `r format(nrow(nottingham_burglary), big.mark = ",")` burglaries and `r format(nrow(nottingham_robbery), big.mark = ",")` robberies in Nottingham, England, in 2022.

```{r}
nottingham_burglary |>
  head(10) |>
  knitr::kable(caption = "`nottingham_burglary`")
```

```{r}
nottingham_robbery |>
  head(10) |>
  knitr::kable(caption = "`nottingham_robbery`")
```

The stand-alone versions of these datasets are gzipped CSV files. The data in these files can be used together with the `nottingham_wards` dataset teach spatial clipping, counting incidents in areas and related topics.


### `nyc_shootings`

```{r}
data(nyc_shootings, package = "crimemappingdata")
```

Dataset of `r format(nrow(nyc_shootings), big.mark = ",")` shootings in New York City recorded by the New York City Police Department (NYPD) in 2019.

```{r}
nyc_shootings |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a CSV file.

This dataset can be used together with the `nyc_precincts` dataset to teach topics such as counting the number of crimes in particular areas.


### `san_francisco_robbery`

```{r}
data(san_francisco_robbery, package = "crimemappingdata")
```

Dataset of `r format(nrow(san_francisco_robbery), big.mark = ",")` personal robberies in San Francisco in 2019.

```{r}
san_francisco_robbery |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a CSV file.


### `vancouver_thefts`

```{r}
data(vancouver_thefts, package = "crimemappingdata")
```

Dataset of `r format(nrow(vancouver_thefts), big.mark = ",")` thefts in the City of Vancouver in 2020.

```{r}
vancouver_thefts |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a gzipped CSV file.



## Area-level crime data


### `germany_violence_counts` and `japan_violence_counts`

```{r}
data(germany_violence_counts, package = "crimemappingdata")
data(japan_violence_counts, package = "crimemappingdata")
```

Datasets of annual counts of different types of violent crime in states of Germany in 2019 and prefectures of Japan in 2012, together with population data and GDP per capita data.

```{r}
germany_violence_counts |>
  head(10) |>
  knitr::kable(caption = "`germany_violence_counts`")
```

```{r}
japan_violence_counts |>
  head(10) |>
  knitr::kable(caption = "`japan_violence_counts`")
```

The format of these datasets is designed to be challenging for students, who will need to reformat the data and wrangle it to create population counts. This is designed to reflect the formats of data that are often provided by statistical agencies.

The stand-alone versions of these datasets are `.rds` files.



### `malaysia_violence_counts`

```{r}
data(malaysia_violence_counts, package = "crimemappingdata")
```

Dataset of annual counts of five types of violent crime in states of Malaysia from 2006 to 2017.

```{r}
malaysia_violence_counts |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a `.rds` file.


### `northants_burglary_counts`

```{r}
data(northants_burglary_counts, package = "crimemappingdata")
```

Dataset of counts of burglaries in `r format(nrow(northants_burglary_counts), big.mark = ",")` lower-layer super output areas in Northamptonshire, England, in 2020.

```{r}
northants_burglary_counts |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a `.rds` file.


### `qld_stalking`

```{r}
data(qld_stalking, package = "crimemappingdata")
```

Dataset of `r format(nrow(qld_stalking), big.mark = ",")` annual counts of stalking offences recorded by the Queensland Police Service in police divisions from 2001 to 2022.

```{r}
qld_stalking |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is an Excel (`.xlsx`) file.


### `uttar_pradesh_murders`

```{r}
data("uttar_pradesh_murders", package = "crimemappingdata")
```

Dataset of counts of murders recorded by police in the `r format(nrow(uttar_pradesh_murders), big.mark = ",")` administrative districts of the state of Uttar Pradesh, India, in 2014.

```{r}
uttar_pradesh_murders |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a CSV file.



## Supporting data


### `cdmx_alcaldias`

```{r}
data(cdmx_alcaldias, package = "crimemappingdata")
```

Simple features (SF) object containing the boundaries of the alcaldías (boroughs) of Mexico City.

```{r}
cdmx_alcaldias_head <- sf::st_drop_geometry(cdmx_alcaldias)
cdmx_alcaldias_head$geometry <- "&lt;SF polygon&gt;"

cdmx_alcaldias_head |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a geopackage file.


### `chicago_police_districts`

```{r}
data(chicago_police_districts, package = "crimemappingdata")
```

Simple features (SF) object containing the boundaries of Chicago Police Department districts.

```{r}
chicago_police_districts_head <- sf::st_drop_geometry(chicago_police_districts)
chicago_police_districts_head$geometry <- "&lt;SF polygon&gt;"

chicago_police_districts_head |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a geopackage file.


### `lancashire_districts`, `lancashire_wards`, `northumbria_districts` and `northumbria_wards`

```{r}
data(lancashire_districts, package = "crimemappingdata")
data(lancashire_wards, package = "crimemappingdata")
data(northumbria_districts, package = "crimemappingdata")
data(northumbria_wards, package = "crimemappingdata")
```

Simple features (SF) objects containing the boundaries of local government wards and districts in Lancashire and Northumbria, England. Boundaries are for 2022.

```{r}
lancashire_districts_head <- sf::st_drop_geometry(lancashire_districts)
lancashire_districts_head$geometry <- "&lt;SF polygon&gt;"

lancashire_districts_head |>
  head(10) |>
  knitr::kable(caption = "`lancashire_districts`")
```

```{r}
lancashire_wards_head <- sf::st_drop_geometry(lancashire_wards)
lancashire_wards_head$geometry <- "&lt;SF polygon&gt;"

lancashire_wards_head |>
  head(10) |>
  knitr::kable(caption = "`lancashire_wards`")
```

```{r}
northumbria_districts_head <- sf::st_drop_geometry(northumbria_districts)
northumbria_districts_head$geometry <- "&lt;SF polygon&gt;"

northumbria_districts_head |>
  head(10) |>
  knitr::kable(caption = "`northumbria_districts`")
```

```{r}
northumbria_wards_head <- sf::st_drop_geometry(northumbria_wards)
northumbria_wards_head$geometry <- "&lt;SF polygon&gt;"

northumbria_wards_head |>
  head(10) |>
  knitr::kable(caption = "`northumbria_wards`")
```

The stand-alone versions of `lancashire_districts`/`northumbria_districts` are in geoJSON format and the stand-alone versions of `lancashire_wards`/`northumbria_wards` are geopackage files.


### `lancashire_ward_pop` and `northumbria_ward_pop`

```{r}
data(lancashire_ward_pop, package = "crimemappingdata")
data(northumbria_ward_pop, package = "crimemappingdata")
```

Datasets of usual resident population in 2020 in each local government ward in Lancashire and Northumbria, England. These can be used together with the `lancashire_asb`/`northumbria_asb` and `lancashire_wards`/`northumbria_wards` datasets for teaching non-spatial joining and calculation of area crime rates.

```{r}
lancashire_ward_pop |>
  head(10) |>
  knitr::kable(caption = "`lancashire_ward_pop`")
```

```{r}
northumbria_ward_pop |>
  head(10) |>
  knitr::kable(caption = "`northumbria_ward_pop`")
```

The stand-alone versions of these dataset are Excel (`.xlsx`) files.


### `medellin_metro_lines` and `medellin_metro_stns`

```{r}
data(medellin_metro_lines, package = "crimemappingdata")
data(medellin_metro_stns, package = "crimemappingdata")
```

Simple features (SF) objects containing the locations of metro lines and stations in Medellin, Colombia.

```{r}
medellin_metro_lines_head <- sf::st_drop_geometry(medellin_metro_lines)
medellin_metro_lines_head$geometry <- "&lt;SF polyline&gt;"

medellin_metro_lines_head |>
  head(10) |>
  knitr::kable(caption = "`medellin_metro_lines`")
```

```{r}
medellin_metro_stns |>
  head(10) |>
  knitr::kable(caption = "`medellin_metro_stns`")
```

The stand-alone version of the `medellin_metro_lines` dataset is a zipped shapefile. The `medellin_metro_stn` dataset is a CSV file. 

These datasets can be used together with the `medellin_homicides` dataset to teach topics such as finding or counting crimes within a certain distance of a facility (e.g. a metro station).


### `nottingham_wards`

```{r}
data(nottingham_wards, package = "crimemappingdata")
```

Simple features (SF) objects containing the boundaries of local government wards and districts in Nottingham, England. Boundaries are for 2022.

```{r}
nottingham_wards_head <- sf::st_drop_geometry(nottingham_wards)
nottingham_wards_head$geometry <- "&lt;SF polygon&gt;"

nottingham_wards_head |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this file is in geopackage format. The data in these files can be used together with the `nottingham_wards` dataset teach spatial clipping, counting incidents in areas and related topics.


### `nyc_precincts`

```{r}
data(nyc_precincts, package = "crimemappingdata")
```

Dataset of the `r format(nrow(nyc_precincts), big.mark = ",")` police precincts in New York City.

```{r}
nyc_precincts_head <- sf::st_drop_geometry(nyc_precincts)
nyc_precincts_head$geometry <- "&lt;SF polygon&gt;"

nyc_precincts |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a geopackage file.

This dataset can be used together with the `nyc_shootings` dataset to teach topics such as counting the number of crimes in particular areas.


### `qld_police_divisions`

```{r}
data(qld_police_divisions, package = "crimemappingdata")
```

Simple features (SF) object containing the boundaries of divisions of the Queensland Police Service as of 2022.

```{r}
qld_police_divisions_head <- sf::st_drop_geometry(qld_police_divisions)
qld_police_divisions_head$geometry <- "&lt;SF polygon&gt;"

qld_police_divisions_head |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a geopackage file.


### `qld_population`

```{r}
data(qld_population, package = "crimemappingdata")
```

Dataset of usual resident population in 2016 in each Queensland Police Service division area. This can be used together with the `qld_police_divisions` and `qld_stalking` datasets, especially for teaching non-spatial joining and calculation of area crime rates.

```{r}
qld_population |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is gzipped CSV file.


### `uttar_pradesh_districts`

```{r}
data(uttar_pradesh_districts, package = "crimemappingdata")
```

Simple features (SF) object containing boundaries of administrative districts in Uttar Pradesh, India.

```{r}
uttar_pradesh_districts_head <- sf::st_drop_geometry(uttar_pradesh_districts)
uttar_pradesh_districts_head$geometry <- "&lt;SF polygon&gt;"

uttar_pradesh_districts_head |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a geopackage file.


### `uttar_pradesh_population`

```{r}
data("uttar_pradesh_population", package = "crimemappingdata")
```

Dataset of usual resident population in 2011 in each administrative district in Uttar Pradesh. This can be used together with the `uttar_pradesh_districts` and `uttar_pradesh_murders` datasets, especially for teaching non-spatial joining and calculation of area crime rates.

```{r}
uttar_pradesh_population |>
  head(10) |>
  knitr::kable()
```

The stand-alone version of this dataset is a CSV file.


